Re-finding to support a Deep Web Question Answering System

### 2010-03-05 trunk/paper/semsearch10/content/ssq_ranking.tex
Added a foot note for the classes

\subsection{Class Divergence}
\label{sec:ctd}
We employ a measure of compatibility, which we call \textit{class
  divergence}, between a source class and a target class using the
\textit{topological structure} of the context classes in the
ontology. We write $S \prec T$ for the reflexive transitive closure of
the superclass relation. Let $d(P,Q)$ represent the hop distance in
the directed ontology inheritance graph from $P$ to $Q$. The
divergence between a source and target class ranges from zero (for
identical classes) to one (for incompatible classes).  Let $S$ be the
source class, $T$ be the target class, and let $C$ be a common
ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$. The class
divergence between $S$ and $T$, the unnormalized class dissimilarity,
is defined as follows:

\begin{equation}
d_{class}(S, T) = \begin{cases}
0 & if S.{Uri} \equiv T.{Uri}\\
d(S, T)/3h & if S \prec T\\
1 & if T \prec S\\
(d(S,root) + d(S,C) \\ \ \ \ \ + d(T,C))/3h & otherwise
\end{cases}
\end{equation}

where $h$ is three times the height of the ontology tree.

>>>>

\subsection{Class Divergence}
\label{sec:ctd}
We employ a measure of compatibility, which we call \textit{class
  divergence}, between a source class\footnote{We use the term \textit{class} when dealing with our ontological structure, however the terms class and \textit{category} are analogous.} and a target class using the \textit{topological structure} of the context classes in the
ontology. We write $S \prec T$ for the reflexive transitive closure of
the superclass relation. Let $d(P,Q)$ represent the hop distance in
the directed ontology inheritance graph from $P$ to $Q$. The
divergence between a source and target class ranges from zero (for
identical classes) to one (for incompatible classes).  Let $S$ be the
source class, $T$ be the target class, and let $C$ be a common
ancestor class of $S$ and $T$ minimizing $d(S,C) + d(T,C)$. The class
divergence between $S$ and $T$, the unnormalized class dissimilarity,
is defined as follows:

\begin{equation}
d_{class}(S, T) = \begin{cases}
0 & if S.{Uri} \equiv T.{Uri}\\
d(S, T)/(3h) & if S \prec T\\
1 & if T \prec S\\
(d(S,root) + d(S,C) \\ \ \ \ \ + d(T,C))/(3h) & otherwise
\end{cases}
\end{equation}

\noindent where $h$ is the height of the ontology tree.
